Showcase some database functionality

### 2022-09-21 indicators/insectindicators/tutorials/tutorial.Rmd
test

```{r, include = F, eval = F}
# This connects to the gisdatabase with a DBI connection named `con`.
# Use for example dbGetQuery(con, "SELECT * FROM ....") to query the database
postgreSQLConnect(
  host = "gisdata-db.nina.no",
  dbname = "gisdata",
  username = "postgjest",
  password = "gjestpost"
)
```

```{r, include = F, eval = F}
#To log into something with your own user, it's good practice not to store passwords in the script.
##I store the username and passwords in a file in my home folder, that only the owner can read.
#Not the prettiest solution, since I read in the info in plain text, but we delete the objects in the same code chunk so it works. 
##Here I also specify that big integers should be converted to integers in R. 
##There are some functions that don't have support for bigints in R at the moment.

source("~/.rpgpass")

postgreSQLConnect(
  host = "gisdata-db.nina.no",
  dbname = "gisdata",
  username = username,
  password = password,
  bigint  = "integer"
)

rm(list = c("username", "password"))
```

@@

>>>>

@@

```{r}
library(Norimon)
```
```{r}
connect_to_insect_db()
```
